Scoring_questionnaires2021

### 2021-08-21 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

score_DASS <- function(df) {
  DASS_data <- as_tibble(df) %>% # Building this df to make debugging easier
    select("Participant Private ID", DASS_01:DASS_21)

  DASS_score <- tibble(
    "Participant Private ID" = DASS_data$`Participant Private ID`,
    DASS_score_total =         sumvars(.df = DASS_data,
                                       DASS_01:DASS_21),

    # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
    DASS_subscale_depression = sumvars(.df = DASS_data,
                                       DASS_03, DASS_05, DASS_10, DASS_13,
                                       DASS_16, DASS_17, DASS_21),

    # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
    DASS_subscale_anxiety =    sumvars(.df = DASS_data,
                                       DASS_02, DASS_04, DASS_07, DASS_09,
                                       DASS_15, DASS_19, DASS_20),

    # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
    DASS_subscale_stress =     sumvars(.df = DASS_data,
                                       DASS_01, DASS_06, DASS_08, DASS_11,
                                       DASS_12, DASS_14, DASS_18)
  )
  return(DASS_score)
}

@@

>>>>

colnames(db_DASS)
db_DASS1<- db_DASS%>%
  select(c(12,13,16,33:73))

colnames(db_DASS1)

db_DASS2<- db_DASS1%>%
select(c(1:3,seq(4, 44, 2)))

db_DASS2$DASS_08<- db_DASS2$STAI_08

db_DASS2$STAI_08<- NULL

db_DASS3 <- db_DASS2 %>%
  # mutate(DASS_score_total =         rowsum(
  #                                      DASS_01:DASS_21))
  #   
    # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
    mutate(DASSDepression = 2*(DASS_03+ DASS_05+ DASS_10+ DASS_13+
                                       DASS_16+ DASS_17+ DASS_21),
    # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
    DASSAnxiety =    2*(DASS_02+ DASS_04+ DASS_07+ DASS_09+
                                       DASS_15+ DASS_19+ DASS_20),

    # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
    # on gorilla DAS_08 is islabeled STAI_08
    DASSStress =     2*(DASS_01+ DASS_06+ DASS_08+ DASS_11+
                                       DASS_12+ DASS_14+ DASS_18)
    )%>%
  mutate(DASSTotal = DASSDepression+DASSAnxiety+DASSStress)

colnames(db_DASS3)
db_DASS3$completion_code<- db_DASS3$`Participant Completion Code`

db_DASS4<- select(db_DASS3, c(1:2,29,25:28))

@@

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/
```{r}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

BVAQ: 83b1
BPQ: bbc4

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse

score_BPQ <- function(df){

  # Create a new temporary df to store the BPQ data 
  BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID", 
           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28) %>%
    # Recode factors into numerics
    mutate_at(.vars = vars(BAI_01:HHI_28), 
              .funs = recode(Never = 1, 
                             Mild = 2, 
                             Moderate = 3, 
                             Severe = 4, 
                             Debilitating = 5))

  print(BPQ_data)

  # Construct final scores
  BPQ_score <- tibble(
    "Participant Private ID" = BPQ_data$`Participant Private ID`,

    # Body awareness image
    BAI_score = sumvars(.df = BPQ_data, 
                        BAI_01:BAI_26) / 26,

    # Autonomic nervous system response
    ANSR_score = sumvars(.df = BPQ_data,
                         ANSR_01:ANSR_20) / 20,

    # Health history inventory
    HHI_score = sumvars(.df = BPQ_data,
                        HHI_01:HHI_28) / 28
  )

  return(BPQ_score)

}
